---
title: "final"
author: "Rachel Tsong"
date: "11/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(CVTuningCov)
library(MASS)
```

# Simulation

### Generate covariates, intervention indicator, and parameters
```{r}
set.seed(1)

# generate baseline covariates x_1i and x_2i
x1i = rnorm(2000, 0, 1)
x2i = NULL

for(j in 1:length(x1i)){
  x2i[j] = rbinom(1, 1, 1/(1+exp(-0.2-0.2*x1i[j])))
}

# generate intervention indicator z_i
zi = rbinom(2000, 1, 0.5)

# generate covariance matrix
sigma = AR1(4, rho = 0.8)

# generate subject specific random effects
epsilon = mvrnorm(2000, mu = c(0,0,0,0), Sigma = sigma)

```


### Generate Response
```{r}
# set regression coefficients
beta_t = matrix(c(rep(-1, 4), rep(0.5, 4), rep(1, 4), 0.4, -0.2, -0.4, -0.6), nrow = 4, ncol = 4)

# generate probability of response
pi0 = dnorm(x = (beta_t[1,1] + (x1i * beta_t[1,2]) + (x2i * beta_t[1,3]) + (zi * beta_t[1,4]) + epsilon[,1]), 0, 1)
pi1 = dnorm(x = (beta_t[2,1] + (x1i * beta_t[2,2]) + (x2i * beta_t[2,3]) + (zi * beta_t[2,4]) + epsilon[,2]), 0, 1)
pi2 = dnorm(x = (beta_t[3,1] + (x1i * beta_t[3,2]) + (x2i * beta_t[3,3]) + (zi * beta_t[3,4]) + epsilon[,3]), 0, 1)
pi3 = dnorm(x = (beta_t[4,1] + (x1i * beta_t[4,2]) + (x2i * beta_t[4,3]) + (zi * beta_t[4,4]) + epsilon[,4]), 0, 1)

pit = cbind(pi0, pi1, pi2, pi3)

# generate response
yi0 = NULL
yi1 = NULL
yi2 = NULL
yi3 = NULL

for (j in 1:length(pi1)) {
  yi0[j] = rbinom(1,1, pi0[j])
  yi1[j] = rbinom(1,1, pi1[j])
  yi2[j] = rbinom(1,1, pi2[j])
  yi3[j] = rbinom(1,1, pi3[j])
}

yit = cbind(yi0, yi1, yi2, yi3)

```


### Simulate Nonignorable Missing data
```{r}
# set gamma 
gamma_t = matrix(c(-2.5, -2, -2.8, -2.8, rep(0.5,4), rep(-0.5, 5), 
                 -0.25, 0.25, 0.50, 0, -0.25, -0.6, 0.6, 0, 0.5,
                 1.3, -0.5, 0, 0.4, 1.7, 1.7), nrow = 4, ncol = 7)

# generate missing data indicator
Ri0_n = NULL
Ri1_n = NULL
Ri2_n = NULL
Ri3_n = NULL

# t = 0
  logit_pi0_n = gamma_t[1,1] + (x1i * gamma_t[1,2]) + (x2i * gamma_t[1,3]) + (zi * gamma_t[1,4]) +
              (0 * gamma_t[1,5]) + (0 * gamma_t[1,6]) + (yi0 * gamma_t[1,7])
    
  pi0_n = exp(logit_pi0_n) / (1 + exp(logit_pi0_n))
    
  for (j in 1:length(pi0_n)) {Ri0_n[j] = rbinom(1, 1, pi0_n[j])}
  
  
# t = 1
  logit_pi1_n = gamma_t[2,1] + (x1i * gamma_t[2,2]) + (x2i * gamma_t[2,3]) + (zi * gamma_t[2,4]) +
              (Ri0_n * gamma_t[2,5]) + (yi0 * gamma_t[2,6]) + (yi1 * gamma_t[2,7])
    
  pi1_n = exp(logit_pi1_n) / (1 + exp(logit_pi1_n))
    
  for (j in 1:length(pi1_n)) {Ri1_n[j] = rbinom(1, 1, pi1_n[j])}

  
# t = 2
  logit_pi2_n = gamma_t[3,1] + (x1i * gamma_t[3,2]) + (x2i * gamma_t[3,3]) + (zi * gamma_t[3,4]) +
              ((Ri0_n+Ri1_n) * gamma_t[3,5]) + (yi1 * gamma_t[3,6]) + (yi2 * gamma_t[3,7])
    
  pi2_n = exp(logit_pi2_n) / (1 + exp(logit_pi2_n))
    
  for (j in 1:length(pi2_n)) {Ri2_n[j] = rbinom(1, 1, pi2_n[j])}
  
  
# t = 3
  logit_pi3_n = gamma_t[4,1] + (x1i * gamma_t[4,2]) + (x2i * gamma_t[4,3]) + (zi * gamma_t[4,4]) +
              ((Ri0_n+Ri1_n+Ri2_n) * gamma_t[4,5]) + (yi2 * gamma_t[4,6]) + (yi3 * gamma_t[4,7])
    
  pi3_n = exp(logit_pi3_n) / (1 + exp(logit_pi3_n))

  for (j in 1:length(pi3_n)) {Ri3_n[j] = rbinom(1, 1, pi3_n[j])}

```


### Create final data set for nonignorable missing data
```{r}
Yi0_n = if_else(Ri0_n == 0, yi0, NULL)
Yi1_n = if_else(Ri1_n == 0, yi1, NULL)
Yi2_n = if_else(Ri2_n == 0, yi2, NULL)
Yi3_n = if_else(Ri3_n == 0, yi3, NULL)

Yit_n = cbind(Yi0_n, Yi1_n, Yi2_n, Yi3_n)
```


### Simulate Ignorable Missing Data
Set $\gamma_{5t}$ and $\gamma_{6t}$ to equal to 0 so that $P_{it}$ depends only on intervention indicator, the covariates, and the cumulative number of missing visits
```{r}
# generate missing data indicator
Ri0_i = NULL
Ri1_i = NULL
Ri2_i = NULL
Ri3_i = NULL

# t = 0
  logit_pi0_i = gamma_t[1,1] + (x1i * gamma_t[1,2]) + (x2i * gamma_t[1,3]) + (zi * gamma_t[1,4]) + 
                (0 * gamma_t[1,5])
    
  pi0_i = exp(logit_pi0_i) / (1 + exp(logit_pi0_i))
    
  for (j in 1:length(pi0_i)) {Ri0_i[j] = rbinom(1, 1, pi0_i[j])}
  
  
# t = 1
  logit_pi1_i = gamma_t[2,1] + (x1i * gamma_t[2,2]) + (x2i * gamma_t[2,3]) + (zi * gamma_t[2,4]) + 
                (Ri0_i * gamma_t[2,5])
    
  pi1_i = exp(logit_pi1_i) / (1 + exp(logit_pi1_i))
    
  for (j in 1:length(pi1_i)) {Ri1_i[j] = rbinom(1, 1, pi1_i[j])}

  
# t = 2
  logit_pi2_i = gamma_t[3,1] + (x1i * gamma_t[3,2]) + (x2i * gamma_t[3,3]) + (zi * gamma_t[3,4]) + 
                ((Ri0_i+Ri1_i) * gamma_t[3,5])
    
  pi2_i = exp(logit_pi2_i) / (1 + exp(logit_pi2_i))
    
  for (j in 1:length(pi2_i)) {Ri2_i[j] = rbinom(1, 1, pi2_i[j])}
  
  
# t = 3
  logit_pi3_i = gamma_t[4,1] + (x1i * gamma_t[4,2]) + (x2i * gamma_t[4,3]) + (zi * gamma_t[4,4]) +
              ((Ri0_i+Ri1_i+Ri2_i) * gamma_t[4,5])
    
  pi3_i = exp(logit_pi3_i) / (1 + exp(logit_pi3_i))

  for (j in 1:length(pi3_i)) {Ri3_i[j] = rbinom(1, 1, pi3_i[j])}


```

### Create final data set for ignorable missing data
```{r}
Yi0_i = if_else(Ri0_i == 0, yi0, NULL)
Yi1_i = if_else(Ri1_i == 0, yi1, NULL)
Yi2_i = if_else(Ri2_i == 0, yi2, NULL)
Yi3_i = if_else(Ri3_i == 0, yi3, NULL)

Yit_i = cbind(Yi0_i, Yi1_i, Yi2_i, Yi3_i)
```

# Fit ignorable and nonignorable models and compare DIC and LPML
```{r}

```


